### 2014-10-16 Studies/2013_PG_County/Report/PG_Co_Fire.tex
Reports: Additional minor edits

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.1838}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup

>>>>

\begingroup
This publication is available free of charge from:
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{http://dx.doi.org/10.6028/NIST.TN.XXXX}
\endgroup
}

@@

\begingroup
{\bf This publication is available free of charge from:}
\hypersetup{urlcolor=black}
\href{http://dx.doi.org/10.6028/NIST.TN.XXXX}{\bf http://dx.doi.org/10.6028/NIST.TN.XXXX} \\
\endgroup
